More than one Author with different Affiliations

### 2012-04-23 paper/ms.tex
Slight rearrangement of appendix sections

\begin{table}
\begin{center}
\begin{tabular}{c|c|c}
Parameter & Proposal & Notes\\
\hline
$N$ & $N \to N + \delta_N$ & Generate $\delta_N$ new stars from prior given
$(\alpha, \beta)$\\
$N$ & $N \to N - \delta_N$ & Remove $\delta_N$ stars at random\\
$\alpha$ & $\alpha \to \alpha + \delta_\alpha$ & Move stars along with $\alpha$
\\
$\alpha$ & $\alpha \to \alpha + \delta_\alpha$ & Stars fixed, use logHastings
factor \\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Move stars' fluxes along with
$\beta$\\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Stars' fluxes fixed, use
logHastings factor \\
$(x,y)$ & $(x,y) \to (x,y)+(\delta_x, \delta_y)$ & Can move $>1$ star.
Include prior via logH \\
$f$ & $f \to f + \delta_f$ & Can move $>1$ stars' fluxes. Include prior
via logH
\end{tabular}
\end{center}
\caption{All $\delta$ parameters are drawn from multi-scale distibutions such
that the largest steps are of order the prior width, and the smallest steps
are of order $10^{-6}$ times the prior width.}
\end{table}

>>>>

\subsubsection{Proposal Distributions}

\begin{table}
\begin{center}
\begin{tabular}{c|c|c}
Parameter & Proposal & Notes\\
\hline
$N$ & $N \to N + \delta_N$ & Generate $\delta_N$ new stars from prior given
$(\alpha, \beta)$\\
$N$ & $N \to N - \delta_N$ & Remove $\delta_N$ stars at random\\
$\alpha$ & $\alpha \to \alpha + \delta_\alpha$ & Move stars along with $\alpha$
\\
$\alpha$ & $\alpha \to \alpha + \delta_\alpha$ & Stars fixed, use logHastings
factor \\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Move stars' fluxes along with
$\beta$\\
$\beta$ & $\beta \to \beta + \delta_\beta$ & Stars' fluxes fixed, use
logHastings factor \\
$(x,y)$ & $(x,y) \to (x,y)+(\delta_x, \delta_y)$ & Can move $>1$ star.
Include prior via logH \\
$f$ & $f \to f + \delta_f$ & Can move $>1$ stars' fluxes. Include prior
via logH
\end{tabular}
\end{center}
\caption{All $\delta$ parameters are drawn from multi-scale distibutions such
that the largest steps are of order the prior width, and the smallest steps
are of order $10^{-6}$ times the prior width.\label{proposals}}
\end{table}

See Table~\ref{proposals} for a list of current proposal distributions.
